Draft

### 2022-07-26 ms.tex
version 0726; my abstract added; k comments: intro refs, f_duty added

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
W\\
E\\
N\\
X\\
I\\
U\\
L\\
I\\
1\\
2\\
3
\end{abstract}

@@

\vspace{5mm}
\section{Introduction} \label{sec:intro}
The growth of massive black holes (BHs) in galactic nuclei is elegantly related to their luminous accretion phases
across the cosmic time \citep{1982MNRAS.200..115S,1992MNRAS.259..725S}.
Comparing the mass density of massive BHs in the local universe and the mass accreted onto BH inferred from
the integration of the quasar luminosity function based on multi-wavelength observations,
the cosmic BH accretion history and their radiative efficiency are nicely constrained \citet{2002MNRAS.335..965Y}
\red{KI: add more references, Ueda+14, Delvecchio+14, Marconi?, and some Shankar's papers}.

Extrapolation of this argument toward higher redshifts beyond $z\sim$ 6 is limited because of the current capability for
high-$z$ quasar observations \citep{2019BAAS...51c.121F} \red{KI: you could find better reference in this Decadal Survey?}.
Nevertheless,... \red{KI: you could say the current status of $z=6$ QLFs/BHMFs; citing Jiang+16, 18, Willott+10, HSC papers.}
Moreover, in the era of the James Webb Space Telescope (JWST) and forthcoming facilities,
e.g., the Roman Space Telescope (RST) and Euclid,
infrared imaging and spectroscopic observations will unveil a wealth of information on the
high-$z$ quasar properties and their environments 
\citep{2019BAAS...51c..45R, 2019arXiv190205569A, 2011arXiv1110.3193L}. 
Deep surveys of high-$z$ quasars and their host galaxies will shed light on the early BH evolution, 
also help answering the intriguing questions e.g., 
the existence of supermassive BHs in the early universe within one billion year 
\citep{2012Sci...337..544V,2013ASSL..396..293H,2020ARA&A..58...27I}, 
and the establishment of BH-galaxy coevolution 
\red{cite Wang+2013; Venemans+2017, Izumi et al. 2021, Inayoshi+2022 simulation, Habouzit+2022}.

Formation of seed BHs is the starting point to characterize the early assembly of massive BH populations.
Their formation pathway and expected mass range have been extensively investigated by numerical simulations and
semi-analytical studies
%From Pop III star remnants ($10-10^3 ~\Msun$) to direct collapse supermassive stars (10$^4-10^5 ~\Msun$),
%the properties of high-$z$ BH seeds are extensively modeled by simulations and semi-analytical works
%\citep[e.g.,][Toyouchi 2022]{2001ApJ...546..635O,2002Sci...295...93A,2006ApJ...652....6Y,2011MNRAS.416.2748I,
%2012ApJ...756...93H,2013ApJ...778..178H,2014MNRAS.439.3798F,
%2014MNRAS.445L.109I,2014MNRAS.445..544S,2014MNRAS.445..107V,2020MNRAS.499.5960S}.
\red{KI: I think here we should cite more general citations: Begelman+2006; Tanaka \& Haiman 2009; Hirano+14, 15,
Toyouchi+2022, one Natarajan+Volonteri's paper discussing the mass function, Valiante+2018, Sassano+21}
Massive star formation episodes in the early universe is substantially modulated by external environmental effects such as
%factors which modulate the Pop III star formation have been assessed,
(i) H$_2$ photo-dissociating irradiation from nearby galaxies
%irradiation in Lyman-Werner band which photo-dissociates the major coolant $\hh$
\citep{2001ApJ...546..635O,2002ApJ...569..558O,2003Natur.425..812B,2010MNRAS.402.1249S,2014MNRAS.445..544S,2014MNRAS.445..107V}
\red{KI: add Chon+16},
(ii) supersonic baryonic streaming motion that delays gas collapse in halos
\citep{2012MNRAS.424.1335F, 2014MNRAS.439.1092T, 2018ApJ...855...17H} \red{KI: add Inayoshi, Li \& Haiman 18, Schauer +17},
and
(iii) dynamical heating caused by frequent halo mergers and turbulence injection led by cold accretion flows
\citep{2003ApJ...592..645Y, 2019Natur.566...85W} \red{KI: add Latif's Nature paper, Mayer+10 or 15}.
Those effects keep isothermal collapse ($T\sim 8000~{\rm K}$) of massive gas at high accretion rates of $\gtrsim 0.1~\Msunyr$
without vigorous fragmentation \citep{2014MNRAS.445L.109I} \red{KI: add Becerra+15, Latif+16}, and allow supermassive stars
with $\sim 10^5~\Msun$ (presumably seed BHs) to form at the halo centers \red{cite Hosokawa+13, Woods+19?, Schleicher+13, Toyouchi+22}.
Although the conditions required for heavy seed formation are thought to be too stringent to be realized in the typical regions of the early universe
\red{cite Dijkstra+08, Ahn+09, Inayoshi \& Tanaka 15}, recent studies by Lupi+21 and Li+21 found that the heavy-seed formation
can be accelerated in the rare, overdense regions of the universe, where non-linear galaxy clustering boosts the irradiation intensity
and the frequency of halo mergers.
%These factors prevail in some environments at high redshifts and facilitate massive Pop III and even supermassive star formation,
%which contribute to the heavy seed scenario of supermassive BH formation at $z\gtrsim$ 6
%\citep[see a review by][]{2020ARA&A..58...27I}.

\red{Introduction of previous studies on QLFs for high-$z$ populations. mention Yung's paper, Ricarte \& Natarajan paper, recent Finkelstein's paper?
Also, I remember one paper of our former postdoc, Kim.
Also, recent Raffaella's student's paper and "highly-empirical paper" you introduced.
Please add more (I might miss some relevant papers.)}
\blue{
% High-z
}

@@

\subsection{BH mass growth}
\label{sec:model}
% The BH accretion at high redshifts is probed only by snapshots, in their most luminous quasar phase. 
% We have constraints on simulations and observations of lower redshift counterparts.
With BH seeds planted, we grow the BHs with a semi-analytical accretion rate model and study the evolution of the BH mass distribution until $z=6$. 
\blue{(references + discussion)}
The growth model is characterized by a minimal number of free parameters, 
% the quasar accretion is episodic with Eddington ratio variations,
describing the BH mass growth rate $\Mdot$ by
%%%%%%%
%    Eq. 1
%%%%%%%
% \begin{equation*}
%   \label{eq:mdot_1}
%   \Mdot_\bullet = \frac{\lambda f(\Mbh) \Mbh}{t_{\rm S}} ,
% \end{equation*}
\begin{equation}
  \label{eq:mdot}
  \Mdot_\bullet = \lambda f(\Mbh) \Mdot_\mathrm{Edd} ,
\end{equation}
% where $t_{\rm S} = \eta_0  M c^2/L_{\mathrm{Edd}} \approx 45$ Myr,
where $\lambda \equiv L/L_\mathrm{Edd}$ is the Eddington ratio,
and $\Mdot_\mathrm{Edd} \equiv L_{\mathrm{Edd}}/\eta_0 c^2$ is the Eddington accretion rate with a 10\% radiative efficiency of $\eta_0=0.1$ \citep{1973A&A....24..337S},
%Note here we adopt the radiative efficiency $\eta_0 \approx 0.1 $,
%according to the thin accretion disk model \citep{1973A&A....24..337S}, 
which is consistent with the value obtained from the Soltan's argument \citep{1982MNRAS.200..115S,2002MNRAS.335..965Y}.
% The high mass BH should be strangulated by as it grows, 
We define the mass dependent function of $f(\Mbh)$ as 
%
\begin{equation}
f(\Mbh) = \frac{2}{1+\left(\Mbh /M_{\bullet,c} \right)^\delta}, 
\end{equation}
%
where we adopt $M_{\bullet,c}=10^8~\Msun$.
With a positive value of $\delta$, the BH growth at the high mass end is suppressed. \blue{(references, Ueda+14?s)}.
In the limit of $\delta \ll 1$, where $f(\Mbh) \simeq 1$ is approximated independent of $M_{\bullet,c}$, the model reproduces an exponential growth with an $e$-folding timescale of
$t_{\rm S} =  \Mbh/\Mdot_{\mathrm{Edd}} \approx 45$ Myr, well known as the Salpeter timescale \citep{1964ApJ...140..796S}.
%h independent of BH mass.
% In \S~\ref{sec:fitting}, $\delta$ turns out to be close to 0, indicating an exponential grow manner independent of BH mass.
%Then $t_{\rm S} =  M/\Mdot_{\mathrm{Edd}} \approx 45$ Myr is the Salpeter $e$-folding timescale \citep{1964ApJ...140..796S}.

The quasar activity is episodic in nature, with accretion bursts triggered by gas inflows to the galactic nuclei
% \citep[e.g., mergers or disk instabilities, see][]{2005Natur.433..604D,2005ApJ...630..705H}, 
\citep{2005Natur.433..604D,2005ApJ...630..705H}, 
and the accretion rate declines by self-regulating feedback processes \citep[e.g.,][]{2008ApJ...686..815Y,2011ApJ...737...26N} 
or gas consumption \citep{1991MNRAS.248..754P,2005ApJ...634..901Y,2007MNRAS.377L..25K}. 
This ``flickering'' pattern of individual quasar luminosity evolution can be directly translated into the diversity 
in the Eddington ratios of quasar samples. 
We here suppose that the Eddington ratio distribution function $\D P/ \D\ln\lambda$ (ERDF) is characterized
with a Schechter function and the distribution function is independent of redshift 
\citep{2006ApJ...639..700H,2009ApJ...698.1550H}. \red{KI: I slightly modified the previous sentence. Is that what you meant?}
\blue{
  not exactly, what I meant may not be necessary here, but we may discuss later.
}
For type-I AGN populations at low redshifts, the ERDF is characterized with a Schechter function
%Observations also propose that the intrinsic ERDF in lower-$z$ quasars hosted by star forming galaxies follows a Schechter shape, 
\citep{2015MNRAS.447.2085S,2016ApJ...826...12J,2018MNRAS.474.1225A}.
Motivated by those facts, we give the ERDF by a Schechter function with two free parameters $\lambda_0$ and $\alpha$ as
%%%%%%%
%    Eq. 2
%%%%%%%
\begin{equation}
  \label{eq:Pl}
  \frac{\D P}{ \D \ln \lambda} \propto
  \left(\frac{\lambda} {\lambda_0} \right)^\alpha \exp{\left(-\frac{\lambda}{\lambda_0}\right)}.
\end{equation}
The normalization is set so that the integrant of this function over $\lambda_\mathrm{min}(=0.01) \leq \lambda < \infty$ is unity.
%normalized by the total probability above $\lambda_\mathrm{min}$ = 0.01.
The minimum Eddington ratio $\lambda_\mathrm{min}$ is adopted from the simulated evolution of quasar luminosities 
that decrease mildly toward $\lambda \sim 0.1-0.01$ with $\lesssim$ 100 Myr after the peak activity \citep{2011ApJ...737...26N}.
Moreover, a turnover at the lowest value $\lambda\lesssim 0.01-0.001$ in the ERDF is suggested by observations \citep{2018MNRAS.474.1225A}.

To characterize the ERDF for a BH population at any time snapshot together with the episodic 
accretion pattern of individual BHs, 
we introduce a time duration of $\tlife$, during which a single value of $\lambda$ that follows 
the ERDF of Eq.~(\ref{eq:Pl}) is assigned to an accreting BH.
In this way, we give a different growth speed of a BH in every period with a duration of $\tlife$ until $z=6$ 
(the corresponding cosmic age is $t_{\rm H}\simeq 800$ Myr).
This treatment enables us to capture the nature of accretion bursts and avoid an unrealistically 
long-lasting rapid growth phase of a BH.
This phenomenological method introducing a parameter of $\tlife(<t_{\rm H})$ allows us to avoid 
numerous uncertainties in modeling of the galaxy assembly, gas feeding, and BH feedback processes in the quasar 
progenitor halos.
Instead of treating those ingredients implemented in previous semi-analytical models, we extract 
an averaged but fundamental timescale that governs mutual correlation between the BHMF and QLF,
based on direct comparison to those distribution functions for observed high-$z$ quasar population.
%We leave a more detailed discussion to \S~\ref{sec:discussion}.}

@@

In this work, we adopt the obscuration fraction $\fobsc$ given by \citet{2014ApJ...786..104U}, 
converting the hard X-ray luminosity to the 1450 $\mathrm{\AA}$ magnitude with bolometric correction factors of
\begin{equation*}
  f^{\rm bol}_{\rm X} =
  a\left[1+\left(\frac{\log \left(\Lbol / L_\odot\right)}{b}\right)^{c}\right],
\end{equation*}
where $a=10.96$, $b = 11.93$, and $c = 17.79$ \citep[Eq. 2 in ][]{2020A&A...636A..73D}, 
and $f^{\rm bol}_{1450}=4.4$ \citep{2006ApJS..166..470R}.
The obscuration fraction reads 
\begin{equation*}
  \fobsc = \text{min}\lbrace  0.84 , 0.73-0.24\times[ (\log \Lbol/L_\odot) -43.75] \rbrace,
\end{equation*}
following \citet{2014ApJ...786..104U}.
An alternative fitting of $\fobsc$ proposed by \citet{2014MNRAS.437.3550M} from *** \blue{(different sample?)} is 
\begin{equation*}
  \fobsc = 0.56 + \frac{1}{\pi} \text{arctan} \frac{43.89 - (\log \Lbol/L_\odot)}{0.46},
\end{equation*}
we fit the parameters using this prescription and discuss the sensitivity of results to $\fobsc$.
% wli: add more!

%An alternative form proposed by \citet{2014MNRAS.437.3550M} shows a similar dependence of $\fobsc$ with the luminosity,
%but the values somewhat differ from that given by \citet{2014ApJ...786..104U} \red{within a factor of $XXX$ KI: more quantitativelt}.
%Compared with another work by  \citet{2014MNRAS.437.3550M}, this shows a similar decreasing trend with luminosity, 
%and the values are in agreement within a factor of 3.
Here, we neglect the contribution from Compton-thick AGNs with $N_\mathrm{H}>10^{24}$ cm$^{-2}$, 
which are obscured even in the hard X-ray band and show possible dependence on quasar properties.
% and it is currently not warranted to discuss the uncertainties of $\fobsc$.
It is worth noting that the obscured fraction for high-$z$ quasar populations is still under investigation,
and the uncertainties would affect our analyses for fainter quasars.
%with complex conversions between the probes in different observational bands,
% optical and X-ray observations, 
%and is need to be 
%and we may refer to more solid prescriptions of $\fobsc$ in the future.
We leave more comprehensive arguments about the quasar obscuration effect for future work.

@@

For the two cases, the best-fit solutions consistently show a small values of $\delta < 0.01$.
%, which is sufficiently small and should be marginalized out. 
This suggests that in our model assumption, a nearly exponential BH growth pattern is favored. 
% In other words, on average the BH growth can be described as exponential, 
% under the premise that the gas supply is episodical. 
The typical duration of quasar activity is required to be $\tlife \simeq 29$ Myr for both the cases, 
which is $\sim 64\%$ of the $e$-folding time for an exponential growth.
This suggests that accreting seed BHs vary their growth speeds (i.e., the Eddington ratio) 
$\sim 30$ times on average, over the cosmic time of $t_{\rm H}\simeq 800$ Myr at $z\simeq 6$.
The timescale of $\tlife$ also gives a lower bound of the quasar lifetimes of $t_{\rm Q}\sim 1-10$ Myr, 
which are estimated by the measurement of the physical extents of hydrogen Ly$\alpha$ proximity zones 
observed in the rest-frame UV spectra (e.g., Eilers+2018, Davies+ 2019).\red{KI: we need to figure out 
if their $t_Q$ is the quasar age or lifetime, or something else?}
More detailed comparison is discussed in \S\ref{sec:evol}.

>>>>

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
The early evolution of black hole mass function (BHMF) and the quasar luminosity function (QLF)
plays an important role in the establishment of BH-galaxy coevolution at high redshifts ($z\gtrsim$ 6).
However, the accretion and radiation properties of growing BHs in the high-$z$ environments 
still remain a challenge to be explored.
In this work, based on a semi-analytic BH seed formation model, 
we relate the seeding time and BH masses at born with the growth tracks of their parent halos. 
We then construct the mass and luminosity evolution of the BH population with a growth model 
characterizing the episodical BH accretion and Eddington ratio distribution function (ERDF) motivated by observational constraints.
The model parameters are fitted to reproduce the observed BHMF and QLF of the quasar population down to $z\sim$ 6.
Our best-fit models suggest that BHs grow with episodical bursts and quescent phases, with time duration 
typically in units of 20 $\sim$ 30 Myr. 
In the sub-sample of massive BHs with $M\gtrsim 10^8~\Msun$, 
the duty cycle of active accretion phase is $f_{\rm duty}\sim 0.15$, 
boosted from that in the whole population by nearly a factor of two. 
We find that the intrinsic ERDF of the whole quasar population is well presented by a Schechter shape, 
indicating a large number of low Eddington ratio objects missed by the current flux-limited quasar selections.
We give prediction of the early evolution of BHMF and QLF, as well as the growth patterns of individual BHs, 
which will likely be unveied by deep and wide-field surveys with, e.g. 
the James Webb Space Telescope (JWST) and the forthcoming Roman Space Telescope (RST) and Euclid.
\end{abstract}

@@

\vspace{5mm}
\section{Introduction} \label{sec:intro}
The growth of massive black holes (BHs) in galactic nuclei is elegantly related to their luminous accretion phases
across the cosmic time \citep{1982MNRAS.200..115S}%,1992MNRAS.259..725S}.
Comparing the mass density of massive BHs in the local universe and the mass accreted onto BH inferred from
the integration of the quasar luminosity function based on multi-wavelength observations,
the cosmic BH accretion history and their radiative efficiency are nicely constrained 
\citep[e.g.][]{1971ApJ...170..223C,1992MNRAS.259..725S,2002MNRAS.335..965Y,2004MNRAS.351..169M,2008MNRAS.388.1011M,2004MNRAS.354.1020S,
2009ApJ...690...20S,2014MNRAS.439.2736D,2014ApJ...786..104U,2017A&A...600A..64T}.

Extrapolation of this argument toward higher redshifts beyond $z\sim$ 6 is limited because of the current capability for
high-$z$ quasar observations \citep{2013ApJ...768..105M,2016ApJ...829...33Y,2019ApJ...884...30W,2019BAAS...51c.121F}.
% \red{KI: you could find better reference in this Decadal Survey?}.
\red{KI: you could say the current status of $z=6$ QLFs/BHMFs; citing Jiang+16, 18, Willott+10, HSC papers.}
\blue{
Nevertheless, currently the $z\sim 6$ quasar population is well constrained by multiband surveys 
\citep{2008AJ....135.1057J,2010AJ....139..906W,2016arXiv161205560C,2016ApJ...833..222J,2018PASJ...70S..35M,2019ApJ...883..183M,2019AJ....157..168D},
with the quasar luminosity function constructed \citep[e.g.,][]{2018ApJ...869..150M}, 
and the virial BH mass investigated from the Mg II 2798 $\rm{\AA}$ line width where deep spectroscopic measurements are carried out
\citep{2007AJ....134.1150J,2007ApJ...669...32K,2010AJ....140..546W,2018Natur.553..473B,2019ApJ...880...77O,2019ApJ...873...35S}. 
}
Moreover, in the era of the James Webb Space Telescope (JWST) and forthcoming facilities,
e.g., the Roman Space Telescope (RST) and Euclid,
infrared imaging and spectroscopic observations will unveil a wealth of information on the
high-$z$ quasar properties and their environments 
\citep{2019BAAS...51c..45R, 2019arXiv190205569A, 2011arXiv1110.3193L}. 
Deep surveys of high-$z$ quasars and their host galaxies will shed light on the early BH evolution, 
also help answering the intriguing questions e.g., 
the existence of supermassive BHs in the early universe within one billion year 
\citep{2012Sci...337..544V,2013ASSL..396..293H,2020ARA&A..58...27I}, 
and the establishment of BH-galaxy coevolution 
\citep[e.g.,][]{2013ApJ...773...44W,2017ApJ...851L...8V,2021ApJ...914...36I,2022ApJ...927..237I,2022MNRAS.511.3751H}.
% \red{cite Wang+2013; Venemans+2017, Izumi et al. 2021, Inayoshi+2022 simulation, Habouzit+2022}.

Formation of seed BHs is the starting point to characterize the early assembly of massive BH populations.
Their formation pathway and expected mass range have been extensively investigated by numerical simulations and
semi-analytical studies
%From Pop III star remnants ($10-10^3 ~\Msun$) to direct collapse supermassive stars (10$^4-10^5 ~\Msun$),
%the properties of high-$z$ BH seeds are extensively modeled by simulations and semi-analytical works
%\citep[e.g.,][Toyouchi 2022]{2001ApJ...546..635O,2002Sci...295...93A,2006ApJ...652....6Y,2011MNRAS.416.2748I,
%2012ApJ...756...93H,2013ApJ...778..178H,2014MNRAS.439.3798F,
%2014MNRAS.445L.109I,2014MNRAS.445..544S,2014MNRAS.445..107V,2020MNRAS.499.5960S}.
\citep{2006MNRAS.370..289B,2009ApJ...696.1798T,2012MNRAS.422.2051N,2014ApJ...781...60H,
2015MNRAS.448..568H,2018MNRAS.474.3825V,2021MNRAS.506..613S,2022arXiv220614459T}.
% \red{KI: I think here we should cite more general citations: Begelman+2006; Tanaka \& Haiman 2009; Hirano+14, 15,
% Toyouchi+2022, one Natarajan+Volonteri's paper discussing the mass function, Valiante+2018, Sassano+21}
Massive star formation episodes in the early universe is substantially modulated by external environmental effects such as
%factors which modulate the Pop III star formation have been assessed,
(i) H$_2$ photo-dissociating irradiation from nearby galaxies
%irradiation in Lyman-Werner band which photo-dissociates the major coolant $\hh$
\citep{2001ApJ...546..635O,2002ApJ...569..558O,2003Natur.425..812B,2010MNRAS.402.1249S,2014MNRAS.445..544S,2014MNRAS.445..107V,2016ApJ...832..134C},
% \red{KI: add Chon+16},
(ii) supersonic baryonic streaming motion that delays gas collapse in halos
\citep{2012MNRAS.424.1335F, 2014MNRAS.439.1092T, 2018ApJ...855...17H,2017MNRAS.471.4878S,2018MNRAS.479.4017I},
% \red{KI: add Inayoshi, Li \& Haiman 18, Schauer +17},
and
(iii) dynamical heating caused by frequent halo mergers and turbulence injection led by cold accretion flows
\citep{2003ApJ...592..645Y,2010Natur.466.1082M,2015ApJ...810...51M,2019Natur.566...85W,2022Natur.607...48L}.
% \red{KI: add Latif's Nature paper, Mayer+10 or 15}.
Those effects keep isothermal collapse ($T\sim 8000~{\rm K}$) of massive gas at high accretion rates of $\gtrsim 0.1~\Msunyr$
without vigorous fragmentation \citep{2014MNRAS.445L.109I,2015MNRAS.446.2380B,2016PASA...33...51L},% \red{KI: add Becerra+15, Latif+16}, 
and allow supermassive stars with $\sim 10^5~\Msun$ (presumably seed BHs) to form at the halo centers 
\citep{2013ApJ...778..178H,2013A&A...558A..59S,2019PASA...36...27W,2022arXiv220614459T}.
% \red{cite Hosokawa+13, Woods+19?, Schleicher+13, Toyouchi+22}.
Although the conditions required for heavy seed formation are thought to be too stringent to be realized in the typical regions of the early universe
\citep{2008MNRAS.391.1961D,2009ApJ...695.1430A,2015MNRAS.450.4350I},
% \red{cite Dijkstra+08, Ahn+09, Inayoshi \& Tanaka 15}, 
recent studies by \citet{2021MNRAS.503.5046L} and \citet{2021ApJ...917...60L} found that the heavy-seed formation
can be accelerated in the rare, overdense regions of the universe, where non-linear galaxy clustering boosts the irradiation intensity
and the frequency of halo mergers.
%These factors prevail in some environments at high redshifts and facilitate massive Pop III and even supermassive star formation,
%which contribute to the heavy seed scenario of supermassive BH formation at $z\gtrsim$ 6
%\citep[see a review by][]{2020ARA&A..58...27I}.

\red{Introduction of previous studies on QLFs for high-$z$ populations. mention Yung's paper, Ricarte \& Natarajan paper, recent Finkelstein's paper?
Also, I remember one paper of our former postdoc, Kim.
Also, recent Raffaella's student's paper and "highly-empirical paper" you introduced.
Please add more (I might miss some relevant papers.)}
\blue{
% Haiman \& Loeb 1997.
% High-z
}

@@

\subsection{BH mass growth}
\label{sec:model}
% The BH accretion at high redshifts is probed only by snapshots, in their most luminous quasar phase. 
% We have constraints on simulations and observations of lower redshift counterparts.
With BH seeds planted, we grow the BHs with a semi-analytical accretion rate model and study the evolution of the BH mass distribution until $z=6$. 
\blue{(references + discussion)}
The growth model is characterized by a minimal number of free parameters, 
% the quasar accretion is episodic with Eddington ratio variations,
describing the BH mass growth rate $\Mdot$ by
%%%%%%%
%    Eq. 1
%%%%%%%
% \begin{equation*}
%   \label{eq:mdot_1}
%   \Mdot_\bullet = \frac{\lambda f(\Mbh) \Mbh}{t_{\rm S}} ,
% \end{equation*}
\begin{equation}
  \label{eq:mdot}
  \Mdot_\bullet = \lambda f(\Mbh) \Mdot_\mathrm{Edd} ,
\end{equation}
% where $t_{\rm S} = \eta_0  M c^2/L_{\mathrm{Edd}} \approx 45$ Myr,
where $\lambda \equiv L/L_\mathrm{Edd}$ is the Eddington ratio,
and $\Mdot_\mathrm{Edd} \equiv L_{\mathrm{Edd}}/\eta_0 c^2$ is the Eddington accretion rate with a radiative efficiency of $\eta_0=0.1$ \citep{1973A&A....24..337S},
%Note here we adopt the radiative efficiency $\eta_0 \approx 0.1 $,
%according to the thin accretion disk model \citep{1973A&A....24..337S}, 
which is consistent with the value obtained from the Soltan's argument \citep[e.g.,][]{2002MNRAS.335..965Y,2010ApJ...725..388C}.
% The high mass BH should be strangulated by as it grows, 
\blue{
On the basis of studies on the mass dependence of the radiative efficiency for AGNs at $z\lesssim$ 3 
\citep{2008MNRAS.390..561C,2012ApJ...749..187L,2014ApJ...786..104U}, 
we also introduce a similar functional form which defines the mass dependent function of $f(\Mbh)$ as 
%
\begin{equation}
f(\Mbh) = \frac{2}{1+\left(\Mbh /M_{\bullet,c} \right)^\delta}, 
\end{equation}
%
where we adopt $M_{\bullet,c}=10^8~\Msun$.
With a positive value of $\delta$, the BH growth at the high mass end is suppressed.
%  \blue{(references, Ueda+14?s)}.
}
In the limit of $\delta \ll 1$, where $f(\Mbh) \simeq 1$ is approximated independent of $M_{\bullet,c}$, the model reproduces an exponential growth with an $e$-folding timescale of
$t_{\rm S} =  \Mbh/\Mdot_{\mathrm{Edd}} \approx 45$ Myr, well known as the Salpeter timescale \citep{1964ApJ...140..796S}.
%h independent of BH mass.
% In \S~\ref{sec:fitting}, $\delta$ turns out to be close to 0, indicating an exponential grow manner independent of BH mass.
%Then $t_{\rm S} =  M/\Mdot_{\mathrm{Edd}} \approx 45$ Myr is the Salpeter $e$-folding timescale \citep{1964ApJ...140..796S}.

The quasar activity is episodic in nature, with accretion bursts triggered by gas inflows to the galactic nuclei
% \citep[e.g., mergers or disk instabilities, see][]{2005Natur.433..604D,2005ApJ...630..705H}, 
\citep{2005Natur.433..604D,2005ApJ...630..705H}, 
and the accretion rate declines by self-regulating feedback processes \citep[e.g.,][]{2008ApJ...686..815Y,2011ApJ...737...26N} 
or gas consumption \citep{1991MNRAS.248..754P,2005ApJ...634..901Y,2007MNRAS.377L..25K}. 
This ``flickering'' pattern of individual quasar luminosity evolution can be directly translated into the diversity 
in the Eddington ratios of quasar samples. 
We here suppose that the Eddington ratio distribution function $\D P/ \D\ln\lambda$ (ERDF) is characterized
with a Schechter function and the distribution function is independent of redshift 
\citep{2006ApJ...639..700H,2009ApJ...698.1550H}.
%
For type-I AGN populations at low redshifts, the ERDF is characterized with a Schechter function
%Observations also propose that the intrinsic ERDF in lower-$z$ quasars hosted by star forming galaxies follows a Schechter shape, 
\citep{2015MNRAS.447.2085S,2016ApJ...826...12J,2018MNRAS.474.1225A}.
Motivated by those facts, we give the ERDF by a Schechter function with two free parameters $\lambda_0$ and $\alpha$ as
%%%%%%%
%    Eq. 2
%%%%%%%
\begin{equation}
  \label{eq:Pl}
  \frac{\D P}{ \D \ln \lambda} \propto
  \left(\frac{\lambda} {\lambda_0} \right)^\alpha \exp{\left(-\frac{\lambda}{\lambda_0}\right)}.
\end{equation}
The normalization is set so that the integrant of this function over $\lambda_\mathrm{min}(=0.01) \leq \lambda < \infty$ is unity.
%normalized by the total probability above $\lambda_\mathrm{min}$ = 0.01.
The minimum Eddington ratio $\lambda_\mathrm{min}$ is adopted from the simulated evolution of quasar luminosities 
that decrease mildly toward $\lambda \sim 0.1-0.01$ with $\lesssim$ 100 Myr after the peak activity \citep{2011ApJ...737...26N}.
Moreover, a turnover at the lowest value $\lambda\lesssim 0.01-0.001$ in the ERDF is suggested by observations \citep{2018MNRAS.474.1225A}.

To characterize the ERDF for a BH population at any time snapshot together with the episodic 
accretion pattern of individual BHs, 
we introduce a time duration of $\tlife$, during which a single value of $\lambda$ that follows 
the ERDF of Eq.~(\ref{eq:Pl}) is assigned to an accreting BH.
In this way, we give a different growth speed of a BH in every period with a duration of $\tlife$ until $z=6$ 
(the corresponding cosmic age is $t_{\rm H}\gtrsim 900$ Myr).
This treatment enables us to capture the nature of accretion bursts and avoid an unrealistically 
long-lasting rapid growth phase of a BH.
This phenomenological method introducing a parameter of $\tlife(<t_{\rm H})$ allows us to avoid 
numerous uncertainties in modeling of the galaxy assembly, gas feeding, and BH feedback processes in the quasar 
progenitor halos.
Instead of treating those ingredients implemented in previous semi-analytical models, we extract 
an averaged but fundamental timescale that governs mutual correlation between the BHMF and QLF,
based on direct comparison to those distribution functions for observed high-$z$ quasar population.
%We leave a more detailed discussion to \S~\ref{sec:discussion}.}

@@

In this work, we adopt the obscuration fraction $\fobsc$ given by \citet{2014ApJ...786..104U}, 
converting the hard X-ray luminosity to the 1450 $\mathrm{\AA}$ magnitude with bolometric correction factors of
\begin{equation*}
  f^{\rm bol}_{\rm X} =
  a\left[1+\left(\frac{\log \left(\Lbol / L_\odot\right)}{b}\right)^{c}\right],
\end{equation*}
where $a=10.96$, $b = 11.93$, and $c = 17.79$ \citep[Eq. 2 in ][]{2020A&A...636A..73D}, 
and $f^{\rm bol}_{1450}=4.4$ \citep{2006ApJS..166..470R}.
The obscuration fraction reads 
\begin{equation*}
  \fobsc = \text{min}\lbrace  0.84 , 0.73-0.24\times[ (\log \Lbol/L_\odot) -43.75] \rbrace,
\end{equation*}
following \citet{2014ApJ...786..104U}.
\blue{
An alternative fitting of $\fobsc$ proposed by \citet{2014MNRAS.437.3550M} 
for their X-ray AGN sample with additional optical obscuration classification gives 
\begin{equation*}
  \fobsc = 0.56 + \frac{1}{\pi} \text{arctan} \frac{43.89 - (\log \Lbol/L_\odot)}{0.46}.
\end{equation*}
We also fit the parameters using this prescription and discuss the sensitivity of results to $\fobsc$ in the Appendix.
}

Here, we neglect the contribution from Compton-thick AGNs with $N_\mathrm{H}>10^{24}$ cm$^{-2}$, 
which are obscured even in the hard X-ray band and show possible dependence on quasar properties.
% and it is currently not warranted to discuss the uncertainties of $\fobsc$.
It is worth noting that the obscured fraction for high-$z$ quasar populations is still under investigation,
and the uncertainties would affect our analyses for fainter quasars.
%with complex conversions between the probes in different observational bands,
% optical and X-ray observations, 
%and is need to be 
%and we may refer to more solid prescriptions of $\fobsc$ in the future.
We leave more comprehensive arguments about the quasar obscuration effect for future work.

@@

For the two cases, the best-fit solutions consistently show a small values of $\delta < 0.01$.
%, which is sufficiently small and should be marginalized out. 
This suggests that in our model assumption, a nearly exponential BH growth pattern is favored. 
% In other words, on average the BH growth can be described as exponential, 
% under the premise that the gas supply is episodical. 
The typical duration of quasar activity is required to be $\tlife \simeq 29$ Myr for both the cases, 
which is $\sim 64\%$ of the $e$-folding time for an exponential growth.
This suggests that accreting seed BHs vary their growth speeds (i.e., the Eddington ratio) 
$\sim 30$ times on average, toward the cosmic time of $t_{\rm H} \gtrsim 900$ Myr at $z\simeq 6$.
The timescale of $\tlife$ also gives a lower bound of the quasar lifetimes of $t_{\rm Q}\sim 1-10$ Myr, 
which are estimated by the measurement of the physical extents of hydrogen Ly$\alpha$ proximity zones 
observed in the rest-frame UV spectra (e.g., Eilers+2018, Davies+ 2019).\red{KI: we need to figure out 
if their $t_Q$ is the quasar age or lifetime, or something else?}
More detailed comparison is discussed in \S\ref{sec:evol}.
